### 2020-12-06 doc/manuscript/Dow_SI.Rmd
finished putting in climwin plots

**(a) $T_{max}$**
```{r climwin_rp_tmax_HARV, out.width="100%", echo=FALSE, fig.align="left", fig.cap= climwin_rp_DOY25_HARV_short_caption}
knitr::include_graphics("tables_figures/HF_ring-porous_DOY25.png")
```

**(b) $T_{min}$**

@@

**(a) $T_{max}$**
```{r climwin_dp_tmin_HARV, out.width="100%", echo=FALSE, fig.align="left", fig.cap= climwin_dp_DOY25_HARV_short_caption}
knitr::include_graphics("tables_figures/HF_diffuse-porous_DOY25.png")
```

**(b) $T_{min}$**

>>>>

**(a) $T_{max}$**
```{r climwin_rp_tmax_HARV, out.width="70%", echo=FALSE, fig.align="left"}
knitr::include_graphics("tables_figures/HF_ring-porous_TMAX.png")
```

**(b) $T_{min}$**
```{r climwin_rp_tmin_HARV, out.width="70%", echo=FALSE, fig.align="left", fig.cap= climwin_rp_DOY25_HARV_short_caption}
knitr::include_graphics("tables_figures/HF_ring-porous_TMIN.png")
```

@@

**(a) $T_{max}$**
```{r climwin_dp_tmax_HARV, out.width="70%", echo=FALSE, fig.align="left"}
knitr::include_graphics("tables_figures/HF_diffuse-porous_TMAX.png")
```

**(b) $T_{min}$**
```{r climwin_dp_tmin_HARV, out.width="70%", echo=FALSE, fig.align="left", fig.cap= climwin_dp_DOY25_HARV_short_caption}
knitr::include_graphics("tables_figures/HF_diffuse-porous_TMIN.png")
```
